### 2023-06-13 abstract.tex
up

We investigate and expand upon the notion of resilience as defined in~\cite{DBLP:journals/corr/PrasadZ16,DBLP:journals/corr/abs-2108-00889,DBLP:conf/gg/Ozkan22}, which asks whether a system can reach a safe state in a bounded number of steps whenever it reached a bad state. We introduce a more general definition of resilience and we define three decidability questions for each of type of resilience: The (state-)resilience problem (RP), the bounded (state-)resilience problem (BRP)
and the $k$-(state-)resilience problem (kRP). The (general) resilience problem 
% is the following: let $L_1,L_2 \subseteq S$ be two subsets of states, S is $(L_1,L_2)$-resilient if $\post^*(L_1)	\subseteq \pred^*(L_2)$. 
asks whether a set of safe elements $\Safe$ is reachable for all elements in a set of bad elements $\Bad$. 
We remark that it is an instance of the home space problem defined in the framework of VASS.
State resilience only consider bad elements that are reachable from an initial state, while bounded-resilience and $k$-resilience ask whether safe is reachable in a bounded number of step and $k$ or less steps respectively.

>>>>

We investigate and expand upon the notion of resilience as defined by Okan Özkan and Nick Würdemann~\cite{DBLP:journals/corr/PrasadZ16,DBLP:journals/corr/abs-2108-00889,DBLP:conf/gg/Ozkan22}, which asks whether a system can reach a safe state in a bounded number of steps whenever it reached a bad state. We introduce a more general definition of resilience and we define three decidability questions for each of type of resilience: The (state-)resilience problem (RP), the bounded (state-)resilience problem (BRP)
and the $k$-(state-)resilience problem (kRP). The (general) resilience problem 
% is the following: let $L_1,L_2 \subseteq S$ be two subsets of states, S is $(L_1,L_2)$-resilient if $\post^*(L_1)	\subseteq \pred^*(L_2)$. 
asks whether a set of safe elements $\Safe$ is reachable for all elements in a set of bad elements $\Bad$. 
We remark that it is an instance of the home space problem defined in the framework of VASS.
State resilience only consider bad elements that are reachable from an initial state, while bounded-resilience and $k$-resilience ask whether safe is reachable in a bounded number of step and $k$ or less steps respectively.
